### 2016-06-08 intro.tex
cheers
added task: definiing unlinkability as a security notion
added comment about 'secure sketches'

\heading{Related work. }
\begin{itemize}
\item Niedermayer et al., breaking privacy of secret-hash-function Bloom filters.
\item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{DSN'15: Looks like a real goldmine of related work!}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''. \tsnote{Gives some security definitions for privacy. Quick scan, not super clear what they achieve.}
\item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
\item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
\item S\"{a}rell\"{a} et al., ``BloomCasting: Security in Bloom Filter Based Multicast''.
\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'' (which actually store the set element by storing~$k$ xor-shares, one at each of the hash indices),``oblivious bloom intersection''}
\end{itemize}

>>>>

\heading{Related work. }
\begin{itemize}
\item Niedermayer et al., breaking privacy of secret-hash-function Bloom filters.
\item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{DSN'15: Looks like a real goldmine of related work!}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''. \tsnote{Gives some security definitions for privacy. Quick scan, not super clear what they achieve.}
\item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
\item Bellovin and Cheswick, ``Privacy-Enhanced Searches Using Encrypted Bloom Filters''.
\item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
\item S\"{a}rell\"{a} et al., ``BloomCasting: Security in Bloom Filter Based Multicast''.
\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'' (which actually store the set element by storing~$k$ xor-shares, one at each of the hash indices),``oblivious bloom intersection''}
\item Tarkoma, Rothenberg, Lagerspetz ``Theory and Practice of Bloom Filters in Distributed Systems'' \tsnote{Great high-level coverage.  Only found preprint version though.}
\item Dodis et al. ``Fuzzy Extractors: How to Generate Strong Keys from Biometrics and Other Noisy Data'' \tsnote{Introduces ``secure sketches'', which is a representation of a single-element set that is information theoretically private (up to some function of the min-entropy of the element); only tangentially related to ``sketches'' as defined in the Bloom filter literature.}
\end{itemize}
